Parenting Observational Study

### 2017-06-05 joint_attention/parenting_obs_JA.Rmd
fixed age plots
added age corr

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
theme_set(theme_bw())
```

@@

Reliability.
```{r}
d.raw_rel <- d.raw_rel%>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja)%>%
  select(SID, bids_rel, pja_rel, cja_rel)

@@

psych::ICC(cja_mat, missing = FALSE, alpha = 0.05)
```

@@

@@

@@

>>>>

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(theme_bw())
```

@@

Reliability.
```{r}
d.raw_rel <- d.raw_rel%>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length)%>%
  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

@@

psych::ICC(cja_mat, missing = FALSE, alpha = 0.05)

l_pja_mat <- d.raw_rel%>%
  left_join(d.raw)%>%
  select(pja_length, l_pja_rel)

psych::ICC(l_pja_mat, missing = FALSE, alpha = 0.05)

l_cja_mat <- d.raw_rel%>%
  left_join(d.raw)%>%
  select(cja_length, l_cja_rel)

psych::ICC(l_cja_mat, missing = FALSE, alpha = 0.05)
```

@@

ms_lpja$age_group <- factor(ms_lpja$age_group , levels = c("6","12", "18"))

@@

ms_lcja$age_group <- factor(ms_lcja$age_group , levels = c("6","12", "18"))

@@

Is the duration of joint attention correlated with age in months?

```{r}
cormat <- d %>%
  select(age_months, pja_length, cja_length, total_lja)
rcorr(as.matrix(cormat))

```
